\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{geometry}
\input{glyphtounicode}
\usepackage{pifont}

% Define custom colors
\definecolor{primarycolor}{RGB}{70, 70, 120}
\definecolor{sectioncolor}{RGB}{50, 50, 80}
\definecolor{accentcolor}{RGB}{180, 50, 50}

% Serif font selection for a more professional look
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins for better spacing
\geometry{
  left=0.75in,
  top=0.6in,
  right=0.75in,
  bottom=0.6in,
  footskip=.5cm
}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Enhanced section formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\Large\color{sectioncolor}
}{}{0em}{\MakeUppercase}[\color{primarycolor}\titlerule \vspace{-1pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands with enhanced spacing and formatting
\newcommand{\resumeItem}[1]{
  \item\large{
    {#1 \vspace{2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {\Large\textbf{#1}} & {\large\color{primarycolor}#2} \\
      \textit{\large#3} & \textit{\large #4} \\
    \end{tabular*}\vspace{1pt}
}

% Improved job description with minimal vertical space
\newcommand{\resumeJobDescription}[1]{
  \vspace{-3pt}
  \begin{minipage}[t]{1.0\textwidth}
    \large{#1}
  \end{minipage}
  \vspace{-3pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% Custom list environments with improved spacing and NO left margin
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}, itemsep=1pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, label=\textbullet, itemsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{1pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge\textbf{\textcolor{sectioncolor}{CHUNG HO}}} \\ \vspace{5pt}
    \large \faPhone\ (+84) 906 246 489 $|$ \faEnvelope\ \href{mailto:hmchung92@gmail.com}{hmchung92@gmail.com} $|$ 
    \faLinkedin\ \href{https://www.linkedin.com/in/ho-minh-chung}{linkedin.com/in/ho-minh-chung}
\end{center}

%----------CAREER SUMMARY----------
\section{CAREER SUMMARY}
Results-driven Technical Lead with 10+ years of experience in designing and delivering scalable fintech platforms across digital banking, cloud-native systems, and enterprise software. Expertise in AWS-based serverless architectures, microservices, and high-throughput transaction systems.

Currently serving as Backend Technical Lead at Tyme, one of the world's fastest-growing digital banking groups. Successfully architected and delivered multi-country lending platforms across Southeast Asia and Africa — handling over \$300M in annual loan volume and serving millions of users.

%----------WORK EXPERIENCE----------
\section{WORK EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{Technical Lead}{2021 - Present}
{TymeX - one of the world's fastest-growing digital banking groups}{}

\resumeJobDescription{Led backend architecture and engineering strategy for scalable, cloud-native lending platforms deployed across three countries. Delivered systems handling over \$300M in annual loan volume, serving millions of users and thousands of merchants.}

\resumeItemListStart
\resumeItem{\textbf{Architected a multi-country Merchant Lending Platform} (5 loan products across 3 countries)}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=0pt, topsep=1pt]
    \item Led end-to-end development of a unified merchant lending platform deployed in South Africa, Philippines, and Indonesia.
    \item Built using Python and AWS Serverless Stack (Lambda, API Gateway, DynamoDB, ALB, S3, SQS) to enable cost-effective scalability and rapid deployment cycles.
    \item Integrated with Mambu, CRM, Core Banking, Segment, Datadog, Databricks for real-time analytics and operational visibility.
    \item Led 2 Scrum teams totaling 15+ engineers, defining code quality standards, CI/CD pipelines, and architectural governance frameworks.
\end{itemize}

\resumeItem{\textbf{Designed and delivered the full lifecycle of an Advance Loan Platform}}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=0pt, topsep=1pt]
    \item Led a cross-functional Scrum team to design and ship a full-cycle digital lending solution for TymeBank, serving over 350,000 eligible customers.
    \item Architected a scalable backend system capable of processing 300,000 monthly loan disbursements, with throughput optimized for thousands of transactions per second during peak traffic.
    \item Designed and implemented automated repayment workflows to support efficient collection across over 300,000 active loans per month, ensuring system resilience, low latency, and high fault tolerance.
\end{itemize}

\resumeItem{\textbf{Led solution architecture for a Buy Now Pay Later (BNPL) Platform}}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=0pt, topsep=1pt]
    \item Designed and delivered a scalable BNPL solution for TymeBank in South Africa, enabling instant credit access at both physical and online retail points.
    \item Architected a cloud-native backend using Java/Spring Boot microservices on Amazon EKS, integrated with Kafka, WSO2, Mambu, and Databricks for real-time transaction processing and analytics.
    \item Led a Scrum team to implement core features: customer onboarding, settlement workflows, accounting modules, card-on-file, purchase lifecycle management, and loyalty-based incentive programs.
    \item Delivered a system that scaled rapidly to support 20,000 physical retail stores, 5,000 e-commerce merchants, and over 200,000 onboarded customers.
\end{itemize}
\resumeItemListEnd

\vspace{2pt}

\resumeSubheading
{Software Engineer → Senior Software Engineer → Tech Lead}{2014 - 2021}
{TMA Solutions - one of Vietnam's leading software outsourcing firms}{}

\resumeJobDescription{Progressed from Software Engineer to Tech Lead, delivering enterprise-grade software solutions for global clients such as Nokia, Alcatel-Lucent, Philips, Broadcom Inc., TecAlliance, and more.}

\resumeItemListStart
\resumeItem{\textbf{Designed and led implementation of end-to-end architectures} for 5+ enterprise-scale client engagements}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=0pt, topsep=1pt]
    \item Led full-lifecycle development across multiple domains including telecom, and automotive.
    \item Established technical standards, best practices, and documentation frameworks that improved long-term code quality.
    \item Mentored and led teams of up to 20 developers, providing architectural guidance, hands-on support, and career growth coaching.
\end{itemize}

\resumeItem{\textbf{FleetManager – SaaS Fleet Management Platform}}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=0pt, topsep=1pt]
    \item Led frontend architecture using Angular monorepo, supporting multiple interfaces including Admin Portal and Workshop Portal.
    \item Built RESTful APIs with ASP.NET Web API, integrated with Apache Kafka for event-driven communication, and deployed via Docker + Kubernetes for scalability and resilience.
\end{itemize}

\resumeItem{\textbf{Chatbot \& Enterprise Search Solutions}}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=0pt, topsep=1pt]
    \item Led a team to deliver 4 Google Cloud Search applications for enterprises like Broadcom Inc. and Philips, enabling unified search across internal knowledge bases and business systems.
    \item Implemented full-stack solutions using Java, Spring Framework, RESTful APIs, ReactJS, Google Cloud, Google Cloud Search, and MySQL.
\end{itemize}

\resumeItem{\textbf{Task Center Platform – Network Device Management System}}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=0pt, topsep=1pt]
    \item Replaced a legacy desktop application with a modern web-based system to manage thousands of network devices at scale.
    \item Built a modular, component-driven architecture reused across 10+ admin applications, significantly improving development efficiency.
    \item Developed dynamic UI rendering components, allowing administrators to configure device management forms without code changes.
    \item Created a library of 20 reusable core components, shared libraries, and skeleton apps, reducing average page development time from days to under 3 hours.
    \item Full-stack implementation using Java, Spring Framework, RESTful APIs, Microservices, MySQL, and AngularJS.
\end{itemize}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------SKILLS & EXPERTISE----------
\section{SKILLS \& EXPERTISE}
\resumeItemListStart
\resumeItem{\textbf{Solution Architecture \& Engineering}: Cloud-Native Design, Microservices, Serverless (AWS), Event-Driven Systems, Agile/Scrum}
\resumeItem{\textbf{Cloud \& DevOps}: AWS (Lambda, API Gateway, DynamoDB, EKS), Docker, Kubernetes, CI/CD}
\resumeItem{\textbf{Backend Engineering}: Java, Spring Boot, Python, Kafka, Observability}
\resumeItem{\textbf{Fintech \& Digital Banking}: Lending (BNPL, Merchant Cash Advance), Core Banking Integration, Payment Gateways, Mambu}
\resumeItem{\textbf{Tools}: Git, Jira, Databrick, Datadog, Segment, Angular, React}
\resumeItemListEnd

%----------HONORS & AWARDS----------
\section{HONORS \& AWARDS}
\resumeItemListStart
\resumeItem{\textbf{Top Performance Employee of the Year} – \textit{Tyme}, 2023, 2024}
\resumeItem{\textbf{Top Performing Employee (5 consecutive years)} – \textit{TMA Solutions}, 2016–2020}
\resumeItem{\textbf{Nokia High Performance Award} – \textit{TMA Solutions}, 2015}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=0pt, topsep=1pt]
    \item \textit{Recognized for outstanding technical performance, leadership, and impact across multiple product teams}
\end{itemize}
\resumeItemListEnd

%----------CERTIFICATES----------
\section{CERTIFICATES}
\resumeItemListStart
\resumeItem{\textbf{AWS Certified Solutions Architect – Associate} – \textit{Amazon Web Services}, 2023}
\resumeItem{\textbf{AWS Certified Developer – Associate} – \textit{Amazon Web Services}, 2024}
\resumeItemListEnd

%----------EDUCATION----------
\section{EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading
{Bachelor of Information Technology}{2010 - 2013}
{CTU University}{}
\resumeSubHeadingListEnd

\end{document}